---
title: "More ggplot Figures Peer Review"
output: html_document
---
# Eduardo Rodrigo Ramírez Salgado

## Problem 1

Create the figure in the solution for Problem 1, using the data included in the R Markdown file.

```{r problem_1_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK
library(tidyverse)

set.seed(12345)
var1<-runif(50,0,10)
set.seed(12345)
var2<-var1+rnorm(50,5,2)
set.seed(12345)
var3<- var1*(-rnorm(50,1,.2))

dat1<-tibble(var1,var2,var3)


```



```{r solution_p1,echo=FALSE,message=FALSE}
ggplot(dat1, mapping = aes(x=var1, y=var2)) + 
  geom_point() +
  geom_smooth(colour="blue")
```

## Problem 2

Create the figure in the solution for Problem 2, using the data included in the R Markdown file.

```{r problem_2_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(10)
var1<-runif(50,0,10)
set.seed(10)
var2<-var1+rnorm(50,5,2)
set.seed(10)
var3<- var1*(-rnorm(50,1,.2))

dat2<-tibble(var1,var2,var3)
```


```{r solution_p2,echo=FALSE,message=FALSE}
####Make sure you load any necessary libraries
library(GGally)
####PUT YOUR CODE HERE
##function 1
my_scatter <- function(data, mapping){
  ggplot(data=data, mapping = mapping)+
    geom_jitter(color="yellow")
}
##function 2 
my_density <- function(data, mapping){
  ggplot(data=data, mapping=mapping) +
    geom_density(alpha = 0.5, 
                 fill="blue")
}
##necesitas revisar y correr primero el script funcionesviz_corr
ggpairs(data=dat2, 
        lower = list(continuous=my_scatter),
        diag = list(continuous=my_density))

```

## Problem 3

Create the figure in the solution for Problem 3, using the data included in the R Markdown file.

```{r problem_3_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(12)
var1<-runif(50,0,10)
set.seed(12)
var2<-var1+rnorm(50,5,2)
set.seed(12)
var3<- var1*(-rnorm(50,1,.2))

dat3<-tibble(var1,var2,var3)
```

```{r problem3,echo=FALSE}

####Make sure you load any necessary libraries
library(ggcorrplot)
library(ggthemes)
####PUT YOUR CODE HERE

tab <- cor(dat3)
ggcorrplot(tab, type="lower")

```

## Problem 4

Create the figure in the solution for Problem 4, using the data included in the R Markdown file.

```{r problem_4_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(5678)
var1<-rnorm(10,25,5)
names<-letters[1:10]

dat4<-tibble(names,var1)
```

```{r problem_4,echo=FALSE}

####Make sure you load any necessary libraries
####PUT YOUR CODE HERE
ggplot(dat4, mapping = aes(x=var1, y=reorder(names, var1))) + 
  geom_point(size=5) +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_line(linetype = "dotted",
                                          color="red")) +
  labs(x="variable 1", y="")
```

## Problem 5

Create the figure in the solution for Problem 5, using the data included in the R Markdown file.

```{r problem_5_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(13)
var1<-rnorm(10,25,5)
names<-letters[1:10]

dat5<-tibble(names,var1)
```

```{r problem_5,echo=FALSE}


####Make sure you load any necessary libraries
ggplot(dat5, aes(x=reorder(names, var1), y=var1)) +
  geom_point(size=1) + geom_segment(aes(x=names, xend=names,
                                        y=0, yend=var1)) +
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(x="", y="variable 1")
  
####PUT YOUR CODE HERE

```

## Problem 6

Create the figure in the solution for Problem 6, using the data included in the R Markdown file.

```{r problem_6_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(8)
fiction<-tibble(Genre=rep("Fiction",5),Time=seq(1:5),Total=sample(1:10,5))
set.seed(7)
biography<-tibble(Genre=rep("Biography",5),Time=seq(1:5),Total=sample(1:10,5))
set.seed(9)
mystery<-tibble(Genre=rep("Mystery",5),Time=seq(1:5),Total=sample(1:10,5))

books_checked_out<-bind_rows(fiction,biography,mystery)
```

```{r problem_6,echo=FALSE}


####Make sure you load any necessary libraries
library(gcookbook)
####PUT YOUR CODE HERE
ggplot(books_checked_out, mapping = aes(x=Time, y=Total, fill=Genre))+
  geom_area()
```

## Problem 7

Create the figure in the solution for Problem 7, using the data included in the R Markdown file.

```{r problem_7_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

books_checked_out2 <- books_checked_out %>%
  filter(Time==1 | Time==5) %>%
  pivot_wider(names_from = Time,values_from=Total) %>%
  rename(Time1=`1`,Time5=`5`)
```
   
```{r,problem_7,echo=FALSE,message=FALSE}   


####Make sure you load any necessary libraries
library(ggalt)
####PUT YOUR CODE HERE
ggplot(books_checked_out2, mapping = aes(y=Genre, 
                                        x=Time1,
                                        xend=Time5))+
  geom_dumbbell(
    size = 0.1,
    size_x = 3, 
    size_xend = 3,
    colour = "Black", 
    colour_x = "blue", 
    colour_xend = "red"
  )+ 
  labs(x="", y="Genre")

```

## Problem 8

Create the figure in the solution for Problem 8, using the data included in the R Markdown file.

```{r, problem_8_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

pie_dat<-c(1,2,3,4,5)
```

```{r, problem_8,echo=FALSE}


###HINT: check the Help file for pie to see how to specify the color to the my_color palette

library(RColorBrewer)

my_color<-brewer.pal(5,"Spectral")

####Make sure you load any necessary libraries
pie(pie_dat, col=my_color)
####PUT YOUR CODE HERE

```


