---
title: "Spatial Figures Peer Review"
output: html_document
---
# Eduardo Rodrigo Rmírez Salgado

## Problem 1

Create the following figure, using the data included in the R Markdown file.

```{r problem_1_data,include=FALSE}

library(tidyverse)
library(maps)

####make some data for painting the map

my_world_map <- map_data("world")

countries <- unique(my_world_map$region)

set.seed(987)
some_data_values <- data.frame(

  "region"=countries,
  
  "Score"=runif(252,0,100))



```

```{r problem_1,echo=FALSE,message=FALSE}

####Make sure you install any necessary libraries

####HINT: Use the following code to get the colors right
#scale_fill_distiller(palette=5)

####HINT: make sure you use left_join to combine the data_values above to the world map data in my_world_map

####PUT YOUR CODE HERE
map_datacom <- left_join(my_world_map, some_data_values, by="region")

#scale_fill_gradientn(g) esta es la forma chida
#g <- c("palegreen4", "palegreen3", "palegreen2", "palegreen1", "#palegreen")

ggplot(map_datacom, aes(long, lat, group=group, fill=Score)) +
  geom_polygon(colour = "Black") + scale_fill_distiller(palette = 5)

```

## Problem 2

Create the following figure, using the data included in the R Markdown file.


```{r problem_2_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK
set.seed(15)
Measurement<-rnorm(32,50,1)
```


```{r solution_p2,echo=FALSE,message=FALSE}

####Make sure you load any necessary libraries

####HINT: Use a filter command to get just maps of Costa Rica, Panama, and Nicaragua
kishi <- maps::world.cities
cnp <- filter(my_world_map,region=='Costa Rica' | region=='Panama' | region=='Nicaragua') 

####Hint: Use a filter command to put in points only for cities with a population of greater than 40,000. This should leave you with 32 cities.
cc_panN <- filter(kishi,country.etc=='Costa Rica' | country.etc=='Panama' | country.etc=='Nicaragua') 

cc_panN <- filter(cc_panN, pop > 40000 )


####Hint: Use add_column to attach the "Measurement" variable to your data, and set that to the color aesthetic when you draw the points.
cc_panN <- cbind(cc_panN, Measurement)
####Hint: set the colors for the city points with

####scale_color_distiller(palette=7)

####Hint: set the size of all points to the value 5
ggplot(cnp, aes(long, lat, group=group)) +
  geom_polygon(colour = "black", fill="white") + scale_fill_distiller(palette = 5) + 
  geom_point(data = cc_panN, mapping = aes(x=long,y=lat, group=NULL,
                                           size=1,
                                            color=Measurement)) + scale_color_distiller(palette = 7) + theme_minimal()


```

## Problem 3

Create the following figure, using the data included in the R Markdown file.

Note that the code in the .rmd file will import a set of simple features data for South America. Make sure you install any necessary packages. 

```{r problem_3_data,include=FALSE}

#####INSTALL THESE PACKAGES IF NECESSARY
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(rgeos)

####DO NOT MODIFY
s_america<-ne_countries(scale="medium",continent='south america',returnclass="sf")

```

```{r problem3,echo=FALSE}

####Make sure you load any necessary libraries

####HINT: the s_america object created in the chunk above is a simple features object with many columns. Identify the correct column based on the solution figure and use it to color in the choropleth.

####HINT: Use scale_fill_distiller and palette 10 to the match the colors.
ggplot() + geom_sf(data=s_america, mapping = aes(geometry=geometry,
                                                 fill=pop_est))+
  scale_fill_distiller(palette = 10)
####PUT YOUR CODE HERE

```


